QALY Comparison - Living Wage Intervention

### 2023-11-13 minos/testing/QALY_comparison_energyCrises_diff.Rmd
Added new make targets for the uk synthetic QALY calculations, and pointed the notebooks to the SF12_uk_scaled directory (on arc)

```{r}
# # read in QALY files for baseline and interventions
out.path <- here::here('output', 'glasgow_scaled')
#out.path <- here::here('output', 'default_config')

>>>>

```{r}
# # read in QALY files for baseline and interventions
#out.path <- here::here('output', 'default_config')
#out.path <- here::here('output', 'glasgow_scaled')
out.path <- here::here('output', 'SF12_uk_scaled')

### 2023-11-13 minos/testing/QALY_comparison_livingWage.Rmd
Added new make targets for the uk synthetic QALY calculations, and pointed the notebooks to the SF12_uk_scaled directory (on arc)

```{r}
# # read in QALY files for baseline and interventions
#out.path <- here::here('output', 'default_config')
out.path <- here::here('output', 'glasgow_scaled')

>>>>

```{r}
# # read in QALY files for baseline and interventions
#out.path <- here::here('output', 'default_config')
#out.path <- here::here('output', 'glasgow_scaled')
out.path <- here::here('output', 'SF12_uk_scaled')
